Dependent Object Types

### 2012-07-06 doc/semester/report.tex
fix semantic typo
minor typoes

The terms in DOT consists of variables $x$, $y$, $z$, lambda
abstractions $\abs x T t$, function application $\app t {t'}$, field
selections $t.l$ and object creation expressions $\new x c t$, where
$c$ is a constructor $T_c \ldefs{\seq{l = v}}$.

The types in DOT consists of type selections $p.L$, refinement types
$T \refine z {\seq{D}}$, function types $T \tfun T'$, type intersections
$T \tand T'$, type unions $T \tor T'$, a top type $\Top$, a bottom
type $\Bot$.

@@

Expansion is not preserved by narrowing. Here, we create two type
selections that are mutually recursive in their upper bounds after
narrowing: $z_0.C2$ initially expands, but after narrowing, $z_0.C_2$
expands to what $z_0.A_2$ expands to, which expands to what $z_0.A_1$
expands to, which expands to what $z_0.A_2$ expands to, and thus we
have an infinite expansion. Thus, the last new expression initially
type-checks, but after narrowing, it doesn't because the precise
expansion needed by $\textsc{new}$ cannot be inferred.

@@

Let $T$ be a shorthand for the type:
\begin{align*}
\Top &\mlrefine z {\\
&\ \Ldecl A {\Top \refine z {\mdecl m \Bot \Top}} \Top\\
&\ \Ldecl B \Top \Top\\
&\ \mdecl m {\Top \refine z {\Ldecl B \Top \Top}} \Top\\
}&
\end{align*}

>>>>

The terms in DOT consists of variables $x$, $y$, $z$, lambda
abstractions $\abs x T t$, function applications $\app t {t'}$, field
selections $t.l$ and object creation expressions $\new x c t$, where
$c$ is a constructor $T_c \ldefs{\seq{l = v}}$.

The types in DOT consists of type selections $p.L$, refinement types
$T \refine z {\seq{D}}$, function types $T \tfun T'$, type intersections
$T \tand T'$, type unions $T \tor T'$, a top type $\Top$, and a bottom
type $\Bot$.

@@

Expansion is not preserved by narrowing. Here, we create two type
selections that are mutually recursive in their upper bounds after
narrowing: $z_0.C_2$ initially expands, but after narrowing, $z_0.C_2$
expands to what $z_0.A_2$ expands to, which expands to what $z_0.A_1$
expands to, which expands to what $z_0.A_2$ expands to, and thus we
have an infinite expansion. Thus, the last new expression initially
type-checks, but after narrowing, it doesn't because the precise
expansion needed by $\textsc{new}$ cannot be inferred.

@@

Let $T$ be a shorthand for the type:
\begin{align*}
\Top &\mlrefine z {\\
&\ \Ldecl A {\Top \refine z {\mdecl m \Bot \Top}} \Top\\
&\ \Ldecl B \Top \Top\\
&\ \mdecl m {{z.A} \refine z {\Ldecl B \Top \Top}} \Top\\
}&
\end{align*}
